The effects of uncertain context inference on motor adaptation

### 2022-01-18 adaptation/article/article.tex
Update on Overleaf.

We generalized the inference over the best-fitting internal models to the concept of context inference, which includes all sensory information, in addition to feedback provided by the experimenters or the task. With this, we showed how this seemingly small generalization provides a parsimonious explanation for several experimental phenomena across many experiments in motor adaptation that, up to now, had assumed the existence of multiple mechanisms.

@@

Together with the results by \cite{Heald_Contextual_2021}, our results show that many behavioral phenomena observed across different experiments can be explained by the uncertainty in context inference and its effects on learning and action selection.

@@

>>>>

We generalized the inference over the best-fitting internal models to the concept of context inference, which includes all sensory information, in addition to feedback provided by the experimenters or the task. With this, we showed how this seemingly-simple generalization provides a parsimonious explanation for several experimental phenomena across many experiments in motor adaptation that, up to now, had assumed the existence of multiple mechanisms.

@@

@@

\subsection{Conclusions}
The results we presented in this work show that many behavioral phenomena observed across different experiments can be explained by the uncertainty in context inference and its effects on learning and action selection. Together with the results by \cite{Heald_Contextual_2021}, these results suggest new venues of investigation for future works in motor adaptation and context-dependent behavior.
